Dynamical Properties of Molecular Cloud Complexes in a Redshift 6 Prototypical Galaxy at the Epoch of Reionization

### 2018-09-10 WRITEUP/ms.tex
updated sec 6.2

While it may appear that there is an inconsistency between the high $\alpha_{\rm vir}$
nature of the majority of the molecular gas in \flower and its SFR.
That is, if most of the molecular gas in \flower has high $\alpha_{\rm vir}$, why does it sustain its high SFR of $\sim$100\,\Msun\,yr\pmOne?
This discrepancy can be explained in two ways.
First, our results are limited by the resolution of the simulation, such that, in each MC, there
likely exist multiple smaller-scales molecular structures (e.g., clumps and cores),
as in the classical MC hierarchy. These smaller structures are 
no longer supported by large-scale gravitational potential and differential rotation,
as turbulence has dissipated rapidly on these smaller scales to enable collapse \citep{Clark04a}.
In addition, non-axisymmetric perturbations (e.g., arms) to the gravitational potential
can induce orbit crossing, shocks and dissipation in gas, promoting turbulence dissipation.
Note also that \citet{Pettitt18a} report that the virial parameter could be a poor indicator
for the star-forming capacity of the massive (10$^{5-6}$\,\Msun) ``clouds'' in their simulation. They
do not find any significant correlation between $\alpha_{\rm vir}$ and cloud mass
and the star formation efficiency ($M_*/M_{\rm cl}$).

@@

While first stars and galaxies are cooled predominated via H$_2$ lines.
As shown in the $T-n$ phase plot in Fig. 8 of \citealt{Pallottini17b}, metals also play an important role in the cooling of early galaxies.

>>>>

While it may appear that there is an inconsistency between the high $\alpha_{\rm vir}$
nature of the majority of the molecular gas in \flower and its SFR.
That is, if most of the molecular gas in \flower has high $\alpha_{\rm vir}$, why does it sustain its high SFR of $\sim$100\,\Msun\,yr\pmOne?
This discrepancy can be explained in two ways.
First, our results are limited by the resolution of the simulation, such that, in each MC, there
likely exist multiple smaller-scales molecular structures (e.g., clumps and cores),
as in the classical MC hierarchy. These smaller structures are 
no longer supported by large-scale gravitational potential and differential rotation,
as turbulence has dissipated rapidly on these smaller scales to enable collapse \citep{Clark04a}.
In addition, non-axisymmetric perturbations (e.g., arms) to the gravitational potential
can induce orbit crossing, shocks and dissipation in gas, promoting turbulence dissipation.

We note that in a recent study by \citet{Pettitt18a}, the authors report that the virial parameter could be a poor indicator
for the star-forming capacity of the massive (10$^{5-6}$\,\Msun) ``clouds'' in their simulation. 
In particular, these authors do not find any significant correlation between $\alpha_{\rm vir}$ and cloud mass
and the star formation efficiency ($M_*/M_{\rm cl}$).
Identifying a new diagnostic tool is beyond the scope of this paper. Here, we are more interested in 
comparing the clouds dynamics with observational studies, and thus, 
part of the discussion presented in this paper is based on virial analysis.
But just something to keep in mind.

@@

While first stars and galaxies are cooled predominated via atomic H and H$_2$ lines.
As shown in the $T-n$ phase plot in Fig. 8 of \citealt{Pallottini17b}, 
metals also play an important role in the cooling of the first galaxies soon after the first generation of stars have enriched the surrounding.

Speculatively, the shallower slope found in the CMF for \flower compared to those observed in the nearby Universe may
suggest that ...
